% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{sectsty}
\usepackage{tabularx}
\usepackage{array}
\usepackage{helvet} 

% Set sans-serif as default font family
\renewcommand{\familydefault}{\sfdefault}

% Set your name here
\def\name{Rebecca L. Martinez}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://rebeccalmartinez.github.io/personal\_website/}

% PDF metadata
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {environmental science, field research, education, UCSB, mentorship},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  top=0.75in,
  left=0.75in,
  right=0.75in,
  bottom=0.75in
}

% Section header style: clean line underneath
\newcommand{\sectionheader}[1]{%
  \noindent\textbf{\large #1} \\[-1ex]
  \noindent\rule{\linewidth}{0.4pt}\\[0.8ex]
}

% Customize page headers
\pagestyle{myheadings}
\markright{\footnotesize \name\hspace{1em}\footnotesize}
\thispagestyle{empty}

% Section fonts
\sectionfont{\rmfamily\mdseries\normalsize}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize}

% No paragraph indent
\setlength\parindent{0pt}

% Fixed width for date column
\newlength{\datecolwidth}
\setlength{\datecolwidth}{3.5cm}

% cvitem command: two columns, left aligned text, right aligned date
\newcommand{\cvitem}[2]{%
  \noindent
  \begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X@{\hspace{1em}}>{\raggedleft\arraybackslash}p{\datecolwidth}@{}}
    #1 & #2 \\
  \end{tabularx}
  \vspace{0.2em}
}

% indented paragraph for sub-items (no bullet)
\newcommand{\cvsubitem}[1]{%
  \par\hangindent=1.5em \noindent #1\par
}

\begin{document}

%===========================
% Header with name and contact info
%===========================
\begin{center}
  {\Large\textbf{Rebecca L. Martinez}}\\[0.15em]
   Undergraduate Researcher \textbar\ Student Assistant\\[0.2em]
  Environmental Studies Program \textbar\ University of California, Santa Barbara\\[0.15em]
  \href{mailto:rebecca_martinez@ucsb.edu}{rebecca\_martinez@ucsb.edu} \textbar\
  \href{mailto:martinez.rl@hotmail.com}{martinez.rl@hotmail.com}
\end{center}
\bigskip
%===========================
% Education Section
%===========================
\sectionheader{Education}
\cvitem{\textbf{B.S. in Environmental Studies}, University of California, Santa Barbara}{Expected 2026}
\cvitem{\textbf{A.S. in Biology}, Allan Hancock College \emph{(With honors)}}{Jun 2024}
\cvitem{\textbf{A.A. in Biology}, Allan Hancock College \emph{(With honors)}}{Dec 2023}
\cvitem{\textbf{A.A. in Mathematics and Science}, Allan Hancock College \emph{(With high honors)}}{Jun 2021}
\cvitem{\textbf{IT Fundamentals Certificate}, Allan Hancock College}{Jun 2024}

%===========================
% Awards and Honors Section
%===========================
\sectionheader{Awards and Honors}
\cvitem{Crankstart Transfer Scholarship — \$5,000}{2025}   
\cvitem{2025 UCSB Edison STEM Conference Research Scholarship — \$2000}{2025}  
\cvitem{UCNRS Field Science Fellowship — \$5,000 + \$1,000 project stipend}{2025}  
\cvitem{Bren Environmental Studies Fellows Program — \$600}{2025}  
\cvitem{Gene \& Susan Lucas Undergraduate Research Fund — \$1,000}{2025}   
\cvitem{Wenger Scholarship, UCSB Environmental Studies — \$2,000}{2025}  
\cvitem{UCSB Promise Scholarship — \$60,000 total over 2 years}{2024--2026}  
\cvitem{PEO Foundation Scholarship — \$1,250}{2024}  
\cvitem{UCSB MESA M-STP Program Scholarship — \$500}{2024}   
\cvitem{Capt. G. Allan Hancock Scholarship — \$3,500}{2024}  
\cvitem{Allan Hancock College MESA Scholarship — \$500}{2023}  
\cvitem{Brander Vineyard Scholarship — \$3,000}{2023}  
\cvitem{Brander Vineyard Scholarship — \$1,000}{2022}  
\cvitem{Joan Semelsberger-Roth Scholarship — \$2,000}{2022}  
\cvitem{Joan Semelsberger-Roth Scholarship — \$1,000}{2021}  
\cvitem{Alpha Gamma Sigma Kathleen D. Loly Academic Award — \$800}{2021}   
\cvitem{Alpha Gamma Sigma Aquarius Chapter Leadership Award}{2021}   
\cvitem{Joyce Dendo Veteran Scholarship — \$500}{2021}   
\cvitem{Virginia B. Martinez Memorial Scholarship — \$500}{2021}

%===========================
% Research Experience Section
%===========================
\sectionheader{Research Experience}
\cvitem{\textbf{Undergraduate Researcher}, UC Santa Barbara}{Jan 2025–Present}
\cvitem{\emph{Geologic Nitrogen Inputs to Semi-Arid Soils with and without Mammalian Bioturbation}
Under Dr. Iris Holzer’s guidance, collected and prepared rock samples using rock saw and shatterbox. Prepared powdered samples in foil capsules for isotope analysis.}{}  
\cvitem{\textbf{Research Assistant}, UC Davis Soil Carbon Project}{Mar 2025–Present}
\cvitem{\emph{Soil Carbon Stabilization Study}
Assisted with pit digging, bulk density sampling, and soil auger collection at UCNRS Sedgwick Reserve. Performed USDA soil profile descriptions and applied safe sampling protocols while supporting team morale.}{}  
\cvitem{\textbf{Student Assistant}, UCSB Office of Education Partnerships}{Oct 2024–Present}
\cvitem{Collect data, maintain field sites, repair equipment, updated protocols, and supported project logistics to improve research operations.}{}  
\cvitem{\textbf{Participant}, UCSB–Smithsonian Scholars Program}{Jun-Aug 2023}
\cvitem{Completed advanced field methods and data science training at UCNRS Santa Cruz Island Reserve and Smithsonian Tropical Research Institute (STRI), Panama, including RStudio/PositCloud instruction.}{}

%===========================
% Teaching and Mentorship Section
%===========================
\sectionheader{Teaching and Mentorship}
\cvitem{\textbf{Discussion Leader}, UCSB–Smithsonian ERES Program}{Jun-Sep 2024, 2025}
\cvitem{Assisted udergraduate instruction of RStudio/PositCloud for data manipulation and visualization, mentored students during field workshops at Santa Cruz Island Reserve; trained students on camera traps, Audiomoths, and GPS.}{}  
\cvitem{\textbf{Teaching Assistant}, Allan Hancock College Human Anatomy Open Lab}{Aug 2023–Jun 2024}
\cvitem{Facilitated Friday lab sessions, including setup and breakdown; developed visual study guides, led office hours, and supported human cadaver lab activities.}{}  
\cvitem{\textbf{Tutor}, Academic Resource Center \& STEM Center, Allan Hancock College}{Aug 2019–Jun 2024}
\cvitem{One-on-one, drop-in, and group sessions. Subjects tutored: anatomy, algebra, botany, introductory biology, calculus 1 \& 2, cellular biology, introductory \& general chemistry, microbiology, and physiology.}{}
\cvitem{\hspace{1em}\textbf{Lead Tutor}; trained new tutors, led workshops on study skills and time management, and supported onboarding of staff and faculty.}{Aug 2020– Jun 2024}
\cvitem{\hspace{1em}\textbf{Embedded Tutor}; Hosted review sessions and office hours, helped with grading, and developed study materials for life and physical science courses}{Jan 2020– Jun 2024}

%===========================
% Leadership and Service Section
%===========================
\sectionheader{Leadership and Service}
\cvitem{\textbf{Student Representative}, UC Systemwide Surveys Student Advisory Group}{Sep 2025–Present}
\cvitem{Gained insight into the full survey process, collaborated on strategies to increase student participation,and provided feedback on survey initiatives}{}  
\cvitem{\textbf{Outreach Volunteer}, UCSB Veteran Support Center}{Jan 2024–Present}
\cvitem{Organized networking events to connect veteran students and women veterans within UCSB’s communities.}{}  
\cvitem{\textbf{Science Outreach Volunteer}, Allan Hancock College Life \& Physical Sciences Department}{Jan 2022–Jun 2024}
\cvitem{Designed and facilitated hands-on science activities for local K–12 students; created educational materials and coordinated event logistics.}{}  
\cvitem{\textbf{Student Representative}, Allan Hancock College}{Aug 2021–Jun 2023}
\cvitem{Served as a student representative for faculty and staff hiring committees and Title V Committee to advocate for student needs.}{} 
\cvitem{\textbf{Permanent Member}, Alpha Gamma Sigma Aquarius Honor Society, Allan Hancock College}{Aug 2019–Present}
\cvitem{\hspace{1em}\textbf{Vice President}; Organized meetings and contributed to executive decisions.}{Jan 2020–Jun 2021}
\cvitem{\hspace{1em}\textbf{Community Service Chair}; Led service projects, fundraisers, and developed an online tracking system.}{Aug 2022–Jun 2023}
\cvitem{\textbf{Key Volunteer}, Santa Barbara County Toys for Tots}{Nov 2018–Present}
\cvitem{Coordinated donation efforts and distributed toys to children during holiday seasons.}{}  
\cvitem{\textbf{United States Marine Corps}}{Jun 2005–Oct 2010}
\cvitem{Developed strong discipline, adaptability, and problem-solving under high-pressure conditions.}{}

%===========================
% Presentations Section
%===========================
\sectionheader{Presentations}
\cvitem{Abstract submitted for AGU Fall Meeting: \textit{Geologic Nitrogen Inputs to Semi-Arid Soils with and without Mammalian Bioturbation}, New Orleans, LA.}{Dec 2025}
\cvitem{\textit{Learning from the Ground Up: Mammalian Bioturbators, Soil, \& Undergraduate Education}, UCSB Environmental Studies 55th Anniversary, Santa Barbara, CA.}{Apr 2025}
\cvitem{\textit{Guest Speaker}, Allan Hancock Foundation Honors Gala, Santa Maria, CA}{May 2024}
\cvitem{\textit{Comparison of Species Richness \& Functional Richness Between Barro Colorado Island and Pipeline Road in Panama}, Cal Poly Summer Internship Research Symposium, San Luis Obispo, CA.}{Aug 2023}
\cvitem{\textit{Comparison of Species Richness \& Functional Richness Between Barro Colorado Island and Pipeline Road in Panama}, UCSB Fall Undergraduate Research Showcase, Santa Barbara, CA.}{Nov 2023}

%===========================
% Programs and Affiliations Section
%===========================
\sectionheader{Programs and Affiliations}
\cvitem{Bren–Environmental Studies Fellows Program}{2025–Present} 
\cvitem{Tau Sigma National Honor Society}{2025–Present} 
\cvitem{American Geophysical Union (AGU)}{2025–Present} 
\cvitem{UCSB Promise Scholars}{2024–Present}  
\cvitem{UCSB Letters \& Science Honors Program}{2024–Present} 
\cvitem{PEO Foundation}{2024-Present} 
\cvitem{UCSB Student Veterans Association (SVA)}{2024–Present}  
\cvitem{UCSB–Smithsonian Scholars Program}{2023–Present}  
\cvitem{Alpha Gamma Sigma Honor Society}{2019–Present}  
\cvitem{Association of Colleges for Tutoring \& Learning Assistance (ACTLA)}{2020–Present}  
\cvitem{Lompoc Veteran Advisory Committee (LVAC)}{2018–Present}

\bigskip
%===========================
% Footer with last updated and link
%===========================
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\url{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
